Efficient Coalition Formation for Web Services

### 2013-03-10 papers/coalition/coalition.tex
Changes

TODO on functional and non-functional requirements specially for critial applications \\

The need for highly available and highly responsive services online has called for collaborative communities of these loosely-coupled business services. The idea of web service communities and the way they are engineered to collaborate was proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09, DBLP:journals/internet/BenatallahSD03, Rosario:2008:PQS:1512146.1512290} where web services with similar functionality are grouped together and users send their requests to communities assuring higher service availability and performance than individual web services. These communities are highly available also more resilience to failure since there is no single point of failure in their architecture.

@@

In this paper, we proposed a cooperative game theory based model for aggregation of web services within communities. The solution concepts of cooperative game theory seeks to find most efficient ways of forming coalitions (teams) of agents, maximizing their gain and payoff, and also distributing gain in a fair way to keep coalitions stable by having all agents satisfied. We first propose a representation function for communities of web services based on their qualities and capacities. Using this function we can evaluate the $worth$ of each coalition of web services. Our community managers facing new membership requests, analyses whether the new coalition having the new set of web services will keep the community stable for $all$ web services already residing in the community or not. The community manager will reject the membership requests if it finds out new coalition can be unstable since there can be $any$ subset of web services gaining significantly more by deviating, colluding with new web services and joining other communities. Also web services facing communities, will try to join communities which maximizes their gain, if they find out they can deviate and agin more, they will form new coalitions with other communities. The cooperative game theory solution methods are combinatorial in nature, making them impractical in real world applications; however, using the concepts of group stability we have offered approximation algorithms running in polynomial time providing web services and community owners with applicable and near-optimal decision making mechanisms.

@@

\emph{Proposition: } The folowwing statement is equivalent with convex condition of equation \ref{eq:convex}.
\begin{equation}\label{eq:convex_snow}
v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T), \\ \forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N; 
\end{equation}

>>>>

The need for highly available and highly responsive services online has called for collaborative communities of these loosely-coupled business web services. The idea of web service communities and the way they are engineered to collaborate was proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09, DBLP:journals/internet/BenatallahSD03, Rosario:2008:PQS:1512146.1512290} where web services with similar functionality are grouped together and users send their requests to communities assuring higher service availability and performance than individual web services. These communities are highly available also more resilience to failure since there is no single point of failure in their architecture.

@@

In this paper, we proposed a cooperative game theory based model for aggregation of web services within communities. The solution concepts of cooperative game theory seeks to find most efficient ways of forming coalitions (teams) of agents, maximizing their gain and payoff, and also distributing gain in a fair way to keep coalitions stable by having all agents satisfied. We first propose a representation function for communities of web services based on their qualities and capacities. Using this function we can evaluate the $worth$ of each coalition of web services. Our community managers facing new membership requests, analyses whether the new coalition having the new set of web services will keep the community stable for $all$ web services already residing in the community or not. The community manager will reject the membership requests if it finds out new coalition can be unstable since there can be $any$ subset of web services gaining significantly more by deviating, colluding with new web services and joining other communities. Also web services facing communities, will try to join communities which maximizes their gain, if they find out they can deviate and agin more, they will form new coalitions with other communities. The cooperative game theory solution methods are combinatorial in nature and are NP-complete, making them impractical in real world applications; however, using the concepts of group stability we have offered approximation algorithms running in polynomial time providing web services and community owners with applicable and near-optimal decision making mechanisms.

@@

\emph{Proposition: } The folowwing statement is equivalent with convex condition of equation \ref{eq:convex}.
\\
\\
For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
\begin{equation}\label{eq:convex_snow}
v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
\end{equation}
